---
title: "Music Insights"
author: "Jennifer Griffiths"
output:
  html_notebook: default
  pdf_document: default
---

##First we need to install tidyverse

```{r eval=FALSE, warning=FALSE}
#install.packages("tidyverse")
#install.packages("purrr")
library(tidyverse)
library(dplyr)
library(rvest)

# LOAD THE DATA
survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")

preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")
```



## Inspecting the Data
```{r}
#View Data
View(preferences)
View(survey)

#Count of rows
nrow(preferences)
#Count of columns
ncol(preferences)
```

#Tidy data for Person and FavoriteSong tables
###Changing the name of the columns in Survey dataframe
 
```{r}
# pseudonym
colnames(survey)[colnames(survey) == "What is your pseudonym?" ] <- "pseudonym"

# pseudonym_generator
colnames(survey)[colnames(survey)== "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "pseudonym_generator"

#time_submitted
colnames(survey)[colnames(survey) == "Timestamp" ] <- "time_submitted"

#sex
colnames(survey)[colnames(survey) == "Sex" ] <- "sex"

#academic_major
colnames(survey)[colnames(survey) == "Major" ] <- "academic_major"

#year_born
colnames(survey)[colnames(survey) == "Year you were born (YYYY)" ] <- "year_born"

#academic_level
colnames(survey)[colnames(survey) == "Academic Year" ] <- "academic_level"

#instrument_list
colnames(survey)[colnames(survey) == "Which musical instruments/talents do you play? (Select all that apply)" ] <- "instrument_list"

#favorite_song_artist
colnames(survey)[colnames(survey) == "Artist" ] <- "favorite_song_artist"

#favorite_song
colnames(survey)[colnames(survey) == "Song" ] <- "favorite_song"

#favorite_song_link
colnames(survey)[colnames(survey) == "Link to song (on Youtube or Vimeo)" ] <- "favorite_song_link"

##preferences dataframe
colnames(preferences)[colnames(preferences) == "What was your pseudonym?" ] <- "pseudonym"

```

###Load dplyr and tidyr libraries

```{r}
library("dplyr")
library("tidyr")
```

#Create Tables Using Tibble
##Person Tibble
```{r message=FALSE, warning=FALSE}
Person <- tibble(time_submitted = survey$time_submitted, pseudonym = survey$pseudonym, generator_name =  survey$pseudonym_generator, sex = survey$sex, academic_major = survey$academic_major,year_born = survey$year_born)
```

###Updating the format of date time
```{r}
#load library
library(readr)
#formatting options in help page
?parse_datetime

#Converting 'time_submitted' to POSIX lt(local time)
Person$time_submitted <- as.POSIXlt(parse_datetime(Person$time_submitted, "%m/%d/%y %H:%M"))

#check updated format at index 1
Person$time_submitted[1]
#check portions of updated format at index 1
Person$time_submitted[1]$hour
Person$time_submitted[1]$min

#levels(Person$academic_major) is not currently a factor

# To convert Person$academic_major to a  factor:
Person$academic_major <-as.factor(Person$academic_major)

#Join upper and lower case versions of CINS
levels(Person$academic_major)[levels(Person$academic_major) == "Computer information systems"] <- "Computer Information Systems"

levels(Person$academic_major)
```

##FavoriteSong Tibble
```{r}
FavoriteSong <- tibble(pseudonym = survey$pseudonym, artist =  survey$favorite_song_artist, song = survey$favorite_song, song_link = survey$favorite_song_link )
```

#Tidy data for Ratings table
```{r}
colnames(preferences)
names(preferences)
```

#Using Tidyr to clean up 

```{r}
preferences <-gather(preferences, key = artist_song,"40 crew\tNot Enough", "Arctic Monkeys Arabella","Avatar\tThe Eagle Has Landed","Ben Folds\tStill", "blink-182\tShe's Out Of Her Mind", "brian jonestown massacre / sarabeth tucek\tSeer", "BROCKHAMPTON\tNO HALO", "Brother Ali\tCan't Take That Away", "Daboii\tBeat in a Chokehold", "Daniel Caesar\tOpen Up", "De La Soul\tPatty Dooke", "Dead Kennedys\tKill The Poor",  "Dominic Fike\t3 Nights", "Gorillaz\tAny but here is Humility", "Dream Theater\tA Change of Seasons", "Ed Sheeran\tDive", "General Levy\tIncredible (Remix)", "Hiroyuki Sawano\tS-ave" , "Jai Paul\tDo You Love Her Now",   "Johnny Cash\tWe'll Meet Again",  "Kane Brown\tWhat's Mine is Yours", "Kim Petras\tI dont want it at all" , "Led Zeppelin\tHey Hey What Can I Do", "Marshmello\tOne Thing Right","Matisyahu\tOne Day", "MF DOOM\tPotholderz"  ,  "mozzy\tbladadah" ,    "Oliver Tree\tHurt", "Radiohead\tweird fishes arpeggi","Rick Astley\tNever Going to Give You Up",  "Sia\tElastic Heart" ,   "Sixtoo\tJackals and Vipers in Envy of Man [Album]",  "Snakehips\tEither Way", "Sufjan Stevens\tShould Have Known Better",  "Tame Impala\tPatience",  "The Black Keys\tUnknown Brother",   "The Byrds\tMr. Spaceman" ,   "Tool\tFear Inoculum", "Traffic\tDear Mr. Fantasy" , "Travis Scott\tAstrothunder",  "Virtual Self\tAngel Voices" , "Wheezer\tBuddy Holly", "Rainbow Kitten Surprise\tCocaine Jesus" ,  "40 crew\tNot Enough"   )


```

```{r}
#rename last column to rating
colnames(preferences)[colnames(preferences) == "40 crew\tNot Enough" ] <- "rating"
```

##Ratings Tibble
```{r}
Ratings <- tibble(time_collected = preferences$Timestamp, pseudonym = preferences$pseudonym, artist_song = preferences$artist_song, rating =  preferences$rating )
```

##Set categorical data to factor
```{r}
Ratings$rating <-as.factor(Ratings$rating)
levels(Ratings$rating)
```

```{r}
library(ggplot2)
#ggplot(Ratings, aes(x = rating)) + geom_histogram(binwidth= 1)
# Group Histogram bars by another factor

```

Look at how differently score everything
```{r}
ggplot(Ratings , aes(y = pseudonym, x = rating)) + geom_count() + theme_light() + scale_colour_grey()
```


QueryInner <- inner_join(FavoriteSong, Ratings, by = "pseudonym") 

QueryLeft <- left_join(FavoriteSong, Ratings, by = "pseudonym") 

QueryRight <- right_join(FavoriteSong, Ratings, by = "pseudonym") 

QueryAnti <- anti_join(FavoriteSong, Ratings, by = "pseudonym") 

QueryFull <- full_join(FavoriteSong, Ratings, by = "pseudonym")

QuerySemi <- semi_join(FavoriteSong, Ratings, by = "pseudonym")

```{r}
## Reconcile the difference between single- and double-column format of representing
## a song and its artist
Ratings$artist_song <- str_replace_all(Ratings$artist_song, 
                                       pattern = "\t", 
                                       replacement = " ")
# favorite_song$artist_song <- paste(favorite_song$artist, " ", favorite_song$title)
favorite_rating <- Ratings %>% 
                    left_join(FavoriteSong, by="pseudonym") %>%
                    filter(artist_song==paste(artist,song)) %>%
                    select(pseudonym,artist_song,rating)
print(favorite_rating)
```

```{r}

```